Value-Suppressing Uncertainty Maps

### 2017-09-14 paper/main.tex
Update abstract and intro.

\section{Introduction}
Uncertainty is an inescapable component of collecting, presenting, and using data. A common goal in the communication of uncertainty is promoting \emph{uncertainty-aware decisions}: the audience should be aware of the risks and rewards of certain decisions, modulate their confidence in their conclusions, and perhaps refrain from making a decision at all if there is too much uncertainty.  A way that designers can contribute to this goal is by ensuring that uncertainty information is \emph{well-integrated} with the rest of the data. That is, it should be difficult to discount or ignore the uncertainty in a dataset.

Simultaneous presentation of uncertainty and value necessitates the construction of a bivariate map\,---\,a relation, in terms of visual variables, between 2-tuples $(\text{value}, \text{uncertainty})$ and mark properties. The design of bivariate maps is difficult and, due to the interference and interplay between different visual variables, often leads to maps with few discriminable categories.

In this paper, we contribute \textbf{Value-Suppressing Uncertainty Palettes} (VSUPs) for integrating data and uncertainty information in visualizations.
VSUP intentionally alias together data values with high uncertainty, affording greater discriminability as uncertainty decreases. If traditional bivariate maps are a two-dimensional square, with differing outputs for each combination of value and uncertainty, VSUP can be thought of as arcs: as uncertainty increases, values are mapped to smaller and smaller sets of outputs, culminating in a singularity where all inputs are mapped to an identical, highly uncertain mark regardless of their data value. \figref{fig:example} shows examples of both a more traditional bivariate map and a VSUP.

We describe the motivations behind the use of VSUPs, examples of their utility for decision-making under uncertainty, and assess VSUPs in a crowdsourced experiment. Our experimental results indicate that VSUPs create close integration between uncertainty and data, promoting rapid but cautious decision-making.

\exampleFig
\section{Related Work}

>>>>

\section{Introduction}
Uncertainty is an inescapable component of collecting, analyzing, and presenting data. A common goal in the communication of uncertainty is promoting \emph{uncertainty-aware decisions}: the audience should be aware of the risks and rewards of certain decisions, modulate their confidence in their conclusions, and perhaps refrain from making a decision at all if there is too much uncertainty.  A way that designers can contribute to this goal is by ensuring that uncertainty information is \emph{well-integrated} with the rest of the data. That is, it should be difficult to discount or ignore the uncertainty in a dataset.

Simultaneous presentation of uncertainty and value necessitates the construction of a bivariate map\,---\,a relation, in terms of visual variables, between 2-tuples $(\text{value}, \text{uncertainty})$ and mark properties. Due to the interference and interplay between different visual variables, bivariate maps may suffer from limited discriminability.

In this paper, we contribute \textbf{Value-Suppressing Uncertainty Palettes} (VSUPs) for integrating data and uncertainty information in visualizations.
VSUPs intentionally alias together data values with high uncertainty, affording greater discriminability as uncertainty decreases. Traditional bivariate maps might be thought of as a 2D square, with differing outputs for each combination of value and uncertainty. In contrast, VSUPs can be conceptualized as arcs: as uncertainty increases, values are mapped to smaller and smaller sets of outputs, culminating in a singularity where all inputs are mapped to an identical, highly uncertain mark regardless of data value. \figref{fig:example} shows examples of both a traditional bivariate map and a VSUP.

We describe the motivations for VSUPs, provide examples of their utility for decision-making under uncertainty, and assess VSUPs in a crowdsourced experiment. Our results indicate that VSUPs create close integration between uncertainty and data, promoting rapid but cautious decision-making.

\exampleFig

\section{Related Work}
